---
title: "H24061024_hw10"
output: html_document
---
```{r}
1+1 
3-5 
4*6 
12/4 
3^4 
31%%7 
31%/%7 
``` 
#Elements storage 
##vector 
###use ***c()*** function to collect a list of numbers into a vector
```{r}
x<-c(5,7,8) 
x 
``` 
###vectors can be joined together 
```{r}
y<-c(x,6:1)
y
``` 
###extract elements from vectors 
```{r}
y[5]
y[c(1,3,5)]
y[-2]
y[-(3:5)]
``` 
###vector arithmetic 
```{r}
z<-x-4
z
``` 
```{r}
z*2
z^2
x^z
y%%2:4
``` 
###simple patterned vectors 
```{r}
seq(1,9,by=2)
rep(3,5)
rep(seq(2,6,2),2)
rep(c(1,4),c(3,2))
rep(c(1,2,4),each=3)
``` 
###missing values and other special values 
the missing value symbol is ***NA*** 
```{r}
evens<-NULL
evens[seq(2,10,2)]<-seq(2,10,2)
evens
``` 
a value which is "not a number" is ***NAN***,usually 0/0
```{r}
x<-c(0,7,8)
x/x
``` 
***Inf***,usually 1/0 
```{r}
1/x
``` 
***numeric(0)*** is a numeric vector of length 0 
```{r}
x[0.4]
x[1.8]
``` 
###character vector 
```{r}
x<-c("red","yellow","blue")
y<-c(x,"green")
y
``` 
an attempt to mix data types in a vector will lead to a result that numbers will be converted to the character type 
```{r}
z<-c(y,1)
z
``` 
to take substrings,use ***substr(x,start,stop)*** 
```{r}
substr(z,2,4)
``` 
to concatenate characters 
```{r}
paste(x," flower","s",sep="")
``` 
***collapse*** parameter allows all the components of the resulting vector to be collapsed into a single string 
```{r}
paste(x," flowers",collapse=", ")
``` 
###factors and levels 
```{r}
x<-c("control","treatment","control","test","treatment")
y<-factor(x)
y
``` 
to see the levels 
```{r}
levels(y)
``` 
to see how the levels coded 
```{r}
as.integer(y)
``` 
the original data can be rewrite as 
```{r}
levels(y)[as.integer(y)]
``` 
###other 
to detect where are missing values 
```{r}
is.na(evens)
``` 
##matrix 
```{r}
m<-matrix(1:6,nrow=2,ncol=3)
m
m[1,2]
m[5]
m[1,]
m[,1]
``` 
##array 
```{r}
a<-array(1:24,c(3,4,2))
``` 
##data frame 
```{r}
colors<-c("red","yellow","blue","green")
numbers<-c(1,2,3,4)
c.a.n<-data.frame(colors,numbers,more.n=5:8)
c.a.n
``` 

#Plot statistical graphics 
##high-level 
###barchart
```{r}
barplot(VADeaths)
```

###dotchart 
```{r}
dotchart(VADeaths)
```
 
###piechart
```{r}
pie(VADeaths)
```
 
###histogram
```{r}
hist(VADeaths)
```
 
###box plot
```{r}
boxplot(VADeaths)
```
 
###scatterplot  
```{r}  
plot(VADeaths)  
```  
 
###Normal

***rnorm(n,mean,sd)*** 
```{r}
rnorm(10, -3, 0.5)
```
###QQplot
```{r}
#qqplot(VADeaths)
X <- rnorm(1000)
A <- rnorm(1000)
qqplot(X, A, main="A and X are the same")
B <- rnorm(1000, mean=3, sd=2)
qqplot(X, B, main="B is rescaled X")
C <- rt(1000, df=2)
qqplot(X, C, main="C has heavier tails")
D <- exp(rnorm(1000))
qqplot(X, D, main="D is skewed to the right")
```

##low-level 
###add points
$$
#Plot statistical graphics 
##high-level 
###curve 
```{r}
curve(expr=sin,from=0,to=6*pi)
```
 
###barchart 
```{r}
barplot(VADeaths)
```
 
###dotchart 
```{r}
dotchart(VADeaths)
```
 
###piechart 
```{r}
pie(VADeaths)
```
 
###histogram 
```{r}
hist(VADeaths)
```
 
###box plot 
```{r}
boxplot(VADeaths)
```
 
###scatterplot 
```{r}
plot(VADeaths)
```
 
###QQplot 
```{r}
x<-rnorm(1000)
y<-rnorm(1000)
qqplot(x,y,main="X and Y are the same")
```
 
##low-level 
* points(x,y,...) **adds points**

* lines(x,y,...) **adds line segments**

* text(x,y,labels,..) **adds text into the graph**

* abline(a,b,...) **adds the line y=ax+b**

* abline(h=y,...) **adds a horizontal line**

* abline(v=x,...) **adds a vertical line**

* polygon(x,y,...) **adds a polygon**

* segments(x0,y0,x1,y1,...) **draws line segments**

* arrows(x0,y0,x1,y1,...) **draws arrows**

* symbols(x,y,...) **draws circles,squares,...**

* legend(x,y,legend,...) **draws a legend**

* title(main,sub,xlab,ylab,...) **adds a main title, a sub-title, an x-axis label and a y-axis label**

* mtext(text,side,line,...) **draws text in the margins**

* axis(side,at,labels,...) **adds an axis to the plot**

* box(...) **adds a box around the plot region**

```{r}
par(mar=c(5,5,5,5)+0.1)
plot(c(1,9),c(0,50),type="n",xlab="",ylab="")
text(6,40,"Plot Region")
points(6,20)
text(6,20,"(6,20)",adj=c(0.5,2))
mtext(paste("Margin",1:4),side=1:4,line=3)
mtext(paste("Line",0:4),side=1,line=0:4,at=3,cex=0.6)
mtext(paste("Line",0:4),side=2,line=0:4,at=15,cex=0.6)
mtext(paste("Line",0:4),side=3,line=0:4,at=3,cex=0.6)
mtext(paste("Line",0:4),side=4,line=0:4,at=15,cex=0.6)

```

###Simulation of other random variables 
```{r}
set.seed(23207) # use this to obtain our output
guesses <- runif(20)
correct.answers <- (guesses < 0.2)
correct.answers
table(correct.answers)
```

###Binomial random variables

***dbinom(x, size, prob)***

***P(X = 4) = 0.234, when X is a binomial random variable with m = 6 and p = 0.5.***
```{r}
dbinom(x = 4, size = 6, prob = 0.5)
``` 
***Pbinom(x,size,prob)*** 

***P(X <= 4) = 0.890, where X is the number of heads obtained in six tosses of a fair coin as***
```{r}
pbinom(4, 6, 0.5)
``` 
***The function qbinom() gives the quantiles for the binomial distribution.The 89th percentile of the distribution of X (as defined above) is***
```{r}
qbinom(0.89,6,0.5)
``` 
###rbinom 
***rbinom(n, size, prob)*** 
***Here, size and prob are the binomial parameters, while n is the number of variates generated.***
```{r}
defectives <- rbinom(24, 15, 0.1)
defectives
```
###Poisson random variables
***dpois(x, lambda)***
***Here, lambda is the Poisson rate parameter, while x is the number of Poisson events. The output from the function is the value of P(X = x).***
```{r}
dpois(x = 3, lambda = 0.5)
``` 
***rpois(n, lambda)***
***The parameter n is the number of variates produced, and lambda is as above.***
```{r}
rpois(10, 3.7)
```
###Exponential random numbers
***pexp(q, rate)***
***The output from this is the value of P(T ≤ q), where T is an exponential random variable with parameter rate.***
```{r}
pexp(1, rate = 3)
```
***The R function rexp() can be used to generate n random exponential variates.***
***rexp(n, rate)***
```{r}
servicetimes <- rexp(10, rate = 3)
servicetimes
```

###Matrix 

***matrix(data,nrow,ncol)*** 
```{r}
H3 <- matrix(c(1, 1/2, 1/3, 1/2, 1/3, 1/4, 1/3, 1/4, 1/5), nrow=3)
H3
```
***cbind(d1, d2, ..., dm)*** 
***rbind(d1, d2, ..., dn)***
```{r}
x=matrix(seq(1,6),nrow=3)
x
y=matrix(seq(7,9),nrow=3)
y
a=matrix(seq(9,7),ncol=3)
a
b=matrix(seq(6,1),ncol=3)
b
cbind(x,y)
```
***cbind(a,b) error*** 

***rbind(x,y) error***
```{r}
rbind(a,b)
``` 
###Name of row(column) 

***rownames(matrix)=(row_name)***
***colnames(matrix)=(column_name)***
```{r}
A=matrix(c(1,2,3,4,5,6,7,8,9),nrow=3)
rownames(A)=c("first","second","third")
colnames(A)=c("I","II","III")
A
``` 
###Inverse matrix 

***solve(matrix)*** 
```{r}
x=matrix(c(1,4,2,3),nrow=2)
x
solve(x)
``` 
###Matrix multiplication and inversion
***matrix*matrix isn't the answer we want.As it will like***
```{r}
a=matrix(c(1,2,3,4),ncol=2)
b=matrix(c(1,4,9,16),ncol=2)
a
b
a*b
```
***matrix%*%matrix is what we want***
```{r}
a%*%b
``` 
###Eigenvalues and eigenvectors 

***eigen(matrix) to show eigen vector&value. Use $vectors or $values to show the one you want*** 
```{r}
ans=eigen(a)
ans
ans=(eigen(a)$vectors)
ans
```
#Programming 
##the ***for()*** loop 
***for(name){command}***
```{r}
Fibonacci<-numeric(12)
Fibonacci[1]<-Fibonacci[2]<-1
for (i in 3:12){
  Fibonacci[i]<-Fibonacci[i-2]+Fibonacci[i-1]
}
Fibonacci
``` 
##the ***if()*** statement 
***if (conditon){commands when TRUE}else{commands when FALSE}***
```{r}
x<-3
if (x>2){
  y<-2*x
}else{
  y<-3*x
}
y
``` 
##the ***while()*** loop 
***while(conditon){statements}***
```{r}
Fib1<-1
Fib2<-1
Fibonacci<-c(Fib1,Fib2)
while (Fib2<300){
  Fibonacci<-c(Fibonacci,Fib2)
  oldFib2<-Fib2
  Fib2<-Fib1+Fib2
  Fib1<-oldFib2
}
Fibonacci
``` 